--- 
title: "Literature Collection: HBM and Injury Prevention"
author: "Jobin"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [manual-ref.bib, references.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "A collection a scientific literature on Injury Prevention, with a focus on Human Body Models.  The output format for this example is bookdown::gitbook."
---

# Introduction 

## Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# use knitcitation for citations
library("knitcitations")
cleanbib()
options("citation_format" = "pandoc")
```
