--- 
title: "Literature Collection: HBM and Injury Prevention"
author: "Jobin"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [manual-ref.bib, references.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "A collection a scientific literature on Injury Prevention, with a focus on Human Body Models.  The output format for this example is bookdown::gitbook."
---

# Introduction 

## Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# use knitcitation for citations
library("knitcitations")
cleanbib()
options("citation_format" = "pandoc")
```

<!--chapter:end:index.Rmd-->

# Human Body Models {#hbm}


## New Seat Configurations

- A Human Modelling Study on Occupant Kinematics in Highly Reclined Seats during Frontal Crashes [@Boyle2019]

<!--chapter:end:01-HBM.Rmd-->


# Human experiments {#exp}

## Human volunteers {#Vol}

## Post-mortem human subjects (PMHS) {#PMHS}

- [@Shaw2009] :  Impact Response of Restrained {PMHS} in Frontal Sled Tests: Skeletal Deformation Patterns Under Seat Belt Loading


## Biofidelity

- A Methodology for Generating Objective Targets for Quantitatively Assessing the Biofideltiy of crash test dummies [@Rhule2009]

<!--chapter:end:02-experiments.Rmd-->

# Head Injuries

We describe our methods in this chapter.

<!--chapter:end:03-Head.Rmd-->

# Spine Injuries


## Cervical Spine


## Thoracic Spine


## Lumbar Spine

Lumbar spine injuries in frontal collision

- Burst fractures of the lumbar spine in frontal crashes `r citep("10.1016/j.aap.2013.05.023")`

- Thoracolumbar Spine Fractures in Frontal Impact Crashes [@Pintar2012]

<!--chapter:end:04-Spine.Rmd-->

# Shoulder and Upper Extremity Injuries

We describe our methods in this chapter.

## Shoulder injuries


## Upper Extremity Injuries

<!--chapter:end:05-Upper-Extremity.Rmd-->

# Thoracic Injuries 

Some _significant_ applications are demonstrated in this chapter.

## Rib injuries

- Detailed subject-specific FE rib modeling for fracture prediction [@Iraeus2019]


- GHBMC M50-O:Evaluation of Skeletal and Soft Tissue Contributions to Thoracic Response, Dynamic Frontal Loading Scenarios [@Ramachandra2019]
  - Experimental data: [@Murach2018]





## Soft tissue injuries

<!--chapter:end:06-Thorax.Rmd-->

# Abdomen and Pelvis Injuries

Some _significant_ applications are demonstrated in this chapter.

## Abdomen

## Pelvis



<!--chapter:end:07-Abdomen-Pelvis.Rmd-->

# Lower Extremities

<!--chapter:end:08-Lower-Extremities.Rmd-->

# Other resources



<!--chapter:end:09-summary.Rmd-->

`r if (knitr:::is_html_output()) '
# References {-}
'`
`r write.bibtex(file="references.bib")`

<!--chapter:end:10-references.Rmd-->

